I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-19 Paper/proofs.tex
update proof

				\begin{lemma}
					If $c$ is in the next layer of $b$, $W_{bc}\neq 0$, and $S$ is defined on both $b$ and $c$ and $S(c)\neq 0$, then $W_{bc}S(c)=S(b)$.
				\end{lemma}

				\begin{proof}
					This is proved in the first section. \qed
				\end{proof}

@@

				By definition, for any $b\in D_J$, either $b\in B_{open}$, or $b$ is a constant node: to it, any path from any input node must have zero weight.

@@

					If $S(b)=-1$, then the similar results hold, replacing $\boldsymbol{x}^*_I$ by $\boldsymbol{x}^\sharp_I$. 
				\end{lemma}

>>>>

				\begin{lemma}
					If $c$ is in the next layer after $b$, $S(c)\neq 0, S(b)$ are both defined, and $W_{bc}\neq 0$, then $W_{bc}S(c)=S(b)$.
				\end{lemma}

				\begin{proof}
					This is proved in the first section of appendix. \qed
				\end{proof}

@@

				By definition, for any $b\in D_J$, either $b\in B_{open}$, or $b$ is a constant node:  any path from any input node must have zero weight to it.

@@

					If $S(b)=-1$, then the similar results hold, replacing $\boldsymbol{x}^*_I$ by $\boldsymbol{x}^\sharp_I$, or replacing $\max$ by $\min$. 
				\end{lemma}
